\documentclass{article}
\usepackage{bubblecv}


\begin{document}


\begin{cv}{Anuraj T Sivankutty}{Oracle ATG consultant, Walmart Labs}


\cvsection[summary]{Profile}  %-----------------------------------------------------------

Experienced Senior Software Engineer with 6 years in e-commerce, specializing in crafting Java solutions for leading brands including Walmart and Sephora. Proven expertise in designing, implementing using Spring Boot, Oracle Commerce (ATG). Proficient in customizing ATG OOTB logic, and third-party integrations. Proficient in test-driven development of Spring based Microservices with JUnit, Mockito, and Power Mock. Well-versed in front-end technologies and tooling.


\cvsection[work]{Work experience}  %------------------------------------------------------

\begin{cvevent}[Jan - 2020][present]

\cvname{\textbf{ATG, Microservices Consultant} }

\begin{center}
  \begin{minipage}{0.6\textwidth}
    Company - \textbf{Walmart Labs}
    \vspace{0.1cm}
    
    \textit{Department - Inventory Managment Squad}
  \end{minipage}
  \hfill
  \begin{minipage}{0.35\textwidth}
    \small{09/2023 - Present} \\
    \textbf{Bangalore, India}
  \end{minipage}
\end{center}



    
    \begin{itemize}
        \item  \textbf{Application Owner of 3 applications }- \textbf{Neuron}, File base feed injection framework \textbf{Setu}, a Kafka based inventory injection framework. \textbf{ATG Aux}, handles the inventory feed processing and serves the end user traffic\textbf{.}

        \item \textbf{Led migration}: Directed the shift from Tibco BW to Java, boosting processing speed tenfold (from 20 to 200+ records/sec) for Sams Club's inventory. Saved 100\% in Tibco BW licensing costs 
        \item  \textbf{Built Microservices for Inventory Feed Processing}: Designed and implemented Neuron, a microservice responsible for ingesting inventory feeds for three banners. It seamlessly transfers business-uploaded files to ATG, resulting in a significant decrease in processing time from 5 records per second to over 500 records per second.

        \item  \textbf{Modernized} \textbf{Inventory Handling for stores: }Engineered Setu, a microservice that utilizes Kafka to ingest inventory from distribution centers to ATG, reducing processing time to \~2 minutes compared to the previous file-based approach that took over 10 minutes to process.

         \item  \textbf{ Enhanced application Performance :  } Collaborated  to debug production issues, identify bottlenecks in legacy systems (ATG), optimizing and scaling up system performance.

    \end{itemize}
\end{cvevent}

\begin{cvevent}[November-2018][December-2020]
    \cvname{\textbf{ATG Consultant} }
    %\cvdescription{Walmart ,SAMS Club} {Bangalore, India}
      \begin{center}
      \begin{minipage}{0.6\textwidth}
         Company - \textbf{Walmart Labs}
        \vspace{0.1cm}
        
        \textit{Department - Sams Club (sams.com.mx)}
      \end{minipage}
      \hfill
      \begin{minipage}{0.35\textwidth}
          \small{11/2018 - 12/2020}\\
        \textbf{Bangalore, India}
      \end{minipage}
    \end{center}
    
    \begin{itemize}
        \item  \textbf{Developed key APIs}- for authentication, cart management, and checkout, handling over 60 million daily requests, at Sams Club.

        \item \textbf{Integrated Order-Based Pickup System}: Integrated store's order-based pickup system with ATG in under 10 days, ensuring compliance with COVID-19 safety measures. 
        
        \item  \textbf{Resolved critical production issues}: Resolved production issues such as reducing double charges from over 5 orders a day to zero, minimized nillpicks.

        \item  \textbf{Modernized} \textbf{Inventory Handling for stores: }Engineered Setu, a microservice that utilizes Kafka to ingest inventory from distribution centers to ATG, reducing processing time to \~2 minutes compared to the previous file-based approach that took over 10 minutes to process.
        
    \end{itemize}
\end{cvevent}


\begin{cvevent}[September - 2018][December - 2020]
    \cvname{\textbf{ATG Consultant} }
    %\cvdescription{Walmart , Bangalore, India}

    \begin{center}
      \begin{minipage}{0.6\textwidth}
        Company - \textbf{Walmart Labs}
        \vspace{0.1cm}   
        
        \textit{Department - WalmartEA, OD}
      \end{minipage}
      \hfill
      \begin{minipage}{0.35\textwidth}
          \small{09/2018 - 12/2020}\\
        \textbf{Bangalore, India}
      \end{minipage}
    \end{center}
    
    \begin{itemize}
        \item  \textbf{Led critical initiatives} including the implementation of a catalog feed import service from external systems to ATG and the seamless integration of Openpay payment services by customizing existing OOTB (out-of-the-box) workflows.

    \end{itemize}
\end{cvevent}


\begin{cvevent}[August - 2017][September - 2018]
    \cvname{\textbf{Junior ATG Developer} }
        \begin{center}
      \begin{minipage}{0.6\textwidth}
        Company - \textbf{Sephora}
        \vspace{0.1cm}
        
        \textit{Department - Customer Service, (Sephora.com)}
      \end{minipage}
      \hfill
      \begin{minipage}{0.35\textwidth}
          \small{09/2018-12/2020}\\
        \textbf{Bangalore, India}
      \end{minipage}
    \end{center}
    
    \begin{itemize}

        \item \textbf{ATG L3 Support: }: Provided comprehensive support for ATG production applications, including managing production issue calls, preparing RCA (Root Cause Analysis) documents, identifying system issues, and assigning action items to respective teams
    
        \item  \textbf{Enhanced UI Performance:} Leveraged JavaScript, CSS, and HTML to achieve sub-2-second page load times by implementing efficient JS and lazy loading techniques, replacing slower JSP-based server-side rendering
        
    \end{itemize}
\end{cvevent}



\cvsection[education]{Education}  %------------------------------------------------------

\begin{cvevent}[June-2012][May-2016]
    \cvname{Bachelor of Technology (B. Tech) in Computer Science and Engineering}
    \cvdescription{Government Model Engineering College, Ernakulam}
    \begin{itemize}
        \item CGPA - 6.7
    \end{itemize}
\end{cvevent}

\begin{cvevent}[June-2010][May-2012]
    \cvname{Technical Higher Secondary Education}
    \cvdescription{Government Technical Higher Secondary school, Institute of Human Resources Development}
    \begin{itemize}
        \item SCORE - 85\%
        \item Major in Computer Science and Electronics
    \end{itemize}
\end{cvevent}


\cvsection[volunteer]{Volunteer Experience}  %----------------------------------------------------------

\begin{cvevent}[2019][Present]
    \cvname{Current Treasurer}
    \cvdescription{Metro Arts and Sports Club, Registration No : PTM/TC/339/2015}
    Volunteered for activity coordination, financial record-keeping, and audit leadership. Managed compliance, cultural events, and charity programs.
\end{cvevent}

\cvseparator[2]



\cvsidebar %-----------------------------------------------------------------------------


\cvsection[contact]{Contact}  %----------------------------------------------------------

\begin{cvitem}[Envelope][4]
    \textbf{Email}\\
    \href{mailto:anurajts@outlook.com}{\texttt{anurajts@outlook.com}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][4]
    \textbf{Phone}\\
    \href{tel:+917012353384}{\texttt{+91-7012353384}}\\
    \href{tel:+91-9562266696}{\texttt{+91-9562266696}} 
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Home][4]
    \textbf{Address}\\
    Marathahalli\\ Bangalore, India
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Globe][4]
    \textbf{Website}\\
    \href{https://anuraj.co.in}{\texttt{www.anuraj.co.in}}
\end{cvitem}


\cvsection[skills]{Skills}  %-----------------------------------------------------------

\begin{cvitem}
    Java J2EE
\end{cvitem}

\cvseparator
\begin{cvitem}
    Spring boot
\end{cvitem}
\cvseparator

\begin{cvitem}
Spring integration
\end{cvitem}

\cvseparator
\begin{cvitem}OracleCommerce(ATG) \end{cvitem}

\cvseparator
\begin{cvitem}Hibernate
\end{cvitem}


\cvseparator
\begin{cvitem}
    Unit testing - Mockito, JUnit
\end{cvitem}

\begin{cvitem}
    Automation Testing -TestNG 
\end{cvitem}

\cvseparator
\begin{cvitem}
   JavaScript, Node
\end{cvitem}


\cvseparator
\begin{cvitem}
    OneOps, Jenkins
\end{cvitem}

\cvseparator
\begin{cvitem}
    Debugging
\end{cvitem}


\cvsection[languages]{Languages}  %--------------------------------------------------------

\cvskill{English}{IELTS Band 7}{1.0}
\cvskill{Hindi}{Basic}{0.3}


\end{cv}

\cvfootnote{
    \tiny I consent to the processing of personal data provided in this document for the purpose of the recruitment process, in compliance with the data protection laws of the country where such processing occurs. I acknowledge and consent to the lawful handling of my personal data in accordance with the data protection regulations of the respective country. The information presented in this document is accurate to the best of my knowledge} 

\end{document}
